---
title: "Indices of diversity from NDVI"
author: 'Por: Eduardo Q Marques'
date: "30 de abril de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rasterdiv)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
```

## Process before calculate diversity

Here I use Landsat-5 NDVI from Tanguro Area-1 (year 2011).

```{r pre}
library(rasterdiv)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)

setwd('C:/Users/Eduardo Q Marques/Documents/My Jobs/Doutorado/Deposito/Banco de Dados Tanguro/Tanguro Indices/Landsat/NDVI')

ndvi = raster("LT05_L1TP_224069_20110830_20161007_01_T1_sr_band1.tif")

#Polygon Area1
area1 <-readOGR(dsn = "C:/Users/Eduardo Q Marques/Documents/My Jobs/Doutorado/Deposito/Banco de Dados Tanguro/shapes",layer="Area1")
area1 = spTransform(area1, crs(ndvi))

ndvi = crop(ndvi, area1)
plot(ndvi)
```

## Calculating diversity

```{r calc, results = "hide"}
#Derive Hill’s and Renyi’s indices
#Shannon's Diversity
sha <- Shannon(ndvi,window=9,np=1,na.tolerance=0.1)

#Pielou's Evenness
pie <- Pielou(ndvi,window=9,np=1,na.tolerance=0.1)

#Berger-Parker
ber <- BergerParker(ndvi,window=9,np=1,na.tolerance=0.1)

#Rao's quadratic Entropy
rao <- Rao(ndvi,window=9,np=1,na.tolerance=0.1,dist_m="euclidean",shannon=FALSE)

#Cumulative Residual Entropy
cre <- CRE(ndvi,window=9,np=1,na.tolerance=0.1)

#Hill's numbers
hil <- Hill(ndvi,window=9,np=1,na.tolerance=0.1,alpha=seq(0,2,0.5))

#Renyi
ren <- Renyi(ndvi,window=9,np=1,na.tolerance=0.1,alpha=seq(0,2,0.5))


#Transform output matrices to RasterLayer
shara <- raster(sha,template=ndvi)
piera <- raster(pie,template=ndvi)
berra <- raster(ber,template=ndvi)
raora <- raster(rao,template=ndvi)
crera <- raster(cre,template=ndvi)
hilra <- lapply(hil, function(x) raster(x,template=ndvi))
renra <- lapply(ren, function(x) raster(x,template=ndvi))
```

## Plot diversity

Map result of diversity index calculate:

```{r plots}
#Shannon's Diversity
levelplot(shara,main="Shannon's entropy (9 px-side moving window)")

#Pielou's Evenness
levelplot(piera,main="Pielou's evenness (9 px-side moving window)")

#Berger-Parker' Index
levelplot(berra,main="Berger-Parker's index (9 px-side moving window)")

#Rao's quadratic Entropy
levelplot(crera,main="Rao's quadratic entropy (9 px-side moving window)")

#Cumulative Residual Entropy
levelplot(crera,main="Cumulative Resiudal Entropy (9 px-side moving window)")

#Hill's numbers (alpha=0, 1, 1.5 and 2)
levelplot(stack(hilra),main="Hill's numbers (9 px-side moving window)")

#Renyi' Index (alpha=0, 1, 1.5 and 2)
levelplot(stack(renra),main="Renyi's entropy (9 px-side moving window)")

```

I still don't really know how to discuss this data so I will study it and resolve it over time. So I will need your help in interpreting these results.

Another point I'm thinking of is using only Landsat data to generate these analyzes and maps. Because Landsat had a time series that fills the study well and because Hyperion has the control portion displaced to another forest rescue intact and this breaks the analyzes and maps.
