---
title: "Tanguro Spectral Mixture"
author: 'Por: Eduardo Q Marques'
date: "15 de maio de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(raster)
library(rasterVis)
library(rgdal)
library(viridis)
```

## Load data

```{r load}
library(raster)
library(rasterVis)
library(rgdal)
library(viridis)

setwd('C:/Users/Eduardo Q Marques/Documents/My Jobs/Doutorado/Deposito/Banco de Dados Tanguro/Fraction_Landsat')
dir()

frac = brick("L8_224069_20140705_frac")

area1 = readOGR(dsn = 'C:/Users/Eduardo Q Marques/Documents/My Jobs/Doutorado/Deposito/Banco de Dados Tanguro/Shapes', layer = 'Polygon_A_B_C')
```

## The bands

Fraction images have 7 bands:<br/>
Band 1 - Fractional cover of bare substrate (S), expressed as a percentage (0-100%)<br/>
Band 2 - Fractional cover of photosynthetic vegetation (PV), expressed as a percentage (0-100%)<br/>
Band 3 - Fractional cover of non-photosynthetic vegetation (NPV), expressed as a percentage (0-100%)<br/>
Band 4 - Uncertainty of the S fraction, expressed as the standard deviation of AutoMCU iterations<br/>
Band 5 - Uncertainty of the PV fraction, expressed as the standard deviation of AutoMCU iterations<br/>
Band 6 - Uncertainty of the NPV fraction, expressed as the standard deviation of AutoMCU iterations<br/>
Band 7 - Total error, expressed as the RMSE of the modeled versus observed reflectance signature

```{r plot}
levelplot(frac, margin = FALSE, col.regions = viridis(100))
```

## Tanguro time-series

The images that Sonaira is working on comprise the entire Landsat scene. That way she takes the entire Tanguro farm. When it finishes processing we will have a time series of all Tanguro from 2000 to 2019.

```{r plot2}
area1 = spTransform(area1, crs(frac))
frac = crop(frac, area1)

levelplot(frac, margin = FALSE, col.regions = viridis(100))
```

## NPV

Next week I will have more images and I will try to explore a little more and start some comparisons with the vegetation indices of Landsat and Hyperion.

```{r plot3}
levelplot(frac[[3]], margin = FALSE, col.regions = viridis(100))
```